---
title: "IDS project"
author: "WYX"
date: "2023-11-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


- merge all datasets

```{r}
stay <- read.csv("D:/Study/Rstudio homework/Final-Project/data/Length of Stay.csv")
readmission <- read.csv("D:/Study/Rstudio homework/Final-Project/data/Readmission.csv")
rii <- read.csv("D:/Study/Rstudio homework/Final-Project/data/Relative Index of Inequality.csv")
diagnois <- read.csv("D:/Study/Rstudio homework/Final-Project/data/Diagnosis.csv")

df <- merge(stay, readmission, by=c('FinancialYear', 'HBT', 'Dataset'))
df <- merge(df, rii, by.x=c('FinancialYear', 'HBT', 'Dataset'), by.y=c('FinancialYear', 'Country', 'Dataset'))
df <- merge(df, diagnois, by=c('FinancialYear', 'HBT', 'Dataset'))
```
- Convert the relevant columns to numeric

```{r}
# Convert the relevant columns to numeric
df$PercentageOfReadmissionsWithin133Days <- as.numeric(df$PercentageOfReadmissionsWithin133Days)
df$LengthOfStay <- as.factor(df$LengthOfStay)
```

- Plot 1: Bar plot of Length of Stay vs. Percentage of Readmissions

```{r}
# Load necessary libraries
library(ggplot2)
library(dplyr)
library(corrplot)
library(reshape2)
# Plot 1: Bar plot of Length of Stay vs. Percentage of Readmissions
plot1 <- ggplot(df, aes(x = LengthOfStay, y = PercentageOfReadmissionsWithin133Days)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  labs(x = "Length of Stay", y = "Percentage of Readmissions") +
  ggtitle("Percentage of Readmissions by Length of Stay")
plot1
```

- Scatter plot of Number of Stays vs. Percentage of Readmissions

```{r}
# Plot 2: Scatter plot of Number of Stays vs. Percentage of Readmissions
plot2 <- ggplot(df, aes(x = NumberOfStays, y = PercentageOfReadmissionsWithin133Days)) +
  geom_point(color = "steelblue") +
  labs(x = "Number of Stays", y = "Percentage of Readmissions") +
  ggtitle("Percentage of Readmissions by Number of Stays")
plot2
```

- Box plot of HBT (Health Board Team) vs. Percentage of Readmissions

```{r}
# Plot 3: Box plot of HBT (Health Board Team) vs. Percentage of Readmissions
plot3 <- ggplot(df, aes(x = HBT, y = PercentageOfReadmissionsWithin133Days)) +
  geom_boxplot(fill = "steelblue") +
  labs(x = "HBT", y = "Percentage of Readmissions") +
  ggtitle("Percentage of Readmissions by HBT")
plot3
```

- Compare the distribution of "DischargeCount" across different "HBT" categories.

```{r}
ggplot(df, aes(x = HBT, y = DischargeCount)) +
  geom_boxplot()
```

- Visualize the distribution of "DischargeCount".

```{r}
ggplot(df, aes(x = DischargeCount)) +
  geom_histogram()
```

- Compare the distribution of "PatientsCount" across different "Dataset" categories.

```{r}
ggplot(df, aes(x = Dataset, y = PatientsCount)) +
  geom_violin()
```

- Visualize the composition of "ICD10Codes" within each "FinancialYear"

```{r}
ggplot(df, aes(x = FinancialYear, fill = ICD10Codes)) +
  geom_bar()
```

- Scatter Plot with Trendline

```{r}
ggplot(df, aes(x = Discharges, y = Patients)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```

- Compare the "PercentageOfReadmissionsWithin28Days" and "PercentageOfReadmissionsWithin133Days" for each "FinancialYear"

```{r}
ggplot(df, aes(x = FinancialYear)) +
  geom_bar(aes(y = PercentageOfReadmissionsWithin28Days), position = "dodge", stat = "identity") +
  geom_bar(aes(y = PercentageOfReadmissionsWithin133Days), position = "dodge", stat = "identity", fill = "red")
```

- Find the most correlated variable

```{r}
# Select only the numeric variables
numeric_vars <- sapply(df, is.numeric)
numeric_df <- df[, numeric_vars]

# Calculate the correlation matrix
cor_matrix <- cor(numeric_df)

# Convert the correlation matrix to a long format
melted_cor_matrix <- melt(cor_matrix)

# Plot the correlation matrix as a heatmap
ggplot(melted_cor_matrix, aes(x = Var1, y = Var2, fill = value)) +
  geom_tile() +
  scale_fill_gradient(low = "blue", high = "red") +
  labs(x = "Variables", y = "Variables", title = "Correlation Matrix Heatmap")

# Get the variable most correlated with the target variable
max_corr <- which.max(abs(cor_matrix["PercentageOfReadmissionsWithin133Days", -3]))

# Print the variable name and correlation value
cat("The variable most correlated with the target variable is:", colnames(cor_matrix)[-3][max_corr], "\n")
cat("Correlation value:", cor_matrix["PercentageOfReadmissionsWithin133Days", -3][max_corr], "\n")
```